### 2019-05-31 README.Rmd
Minor documentation fixes, reknit README
Update bibliographical info to JOSS
- Addd badge and rebuild README
- Bump cache to build site with updated pkgdown

[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg){data-external="1"}](https://opensource.org/licenses/MIT)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2630836.svg){data-external="1"}](https://doi.org/10.5281/zenodo.2630836)
[![CircleCI](https://circleci.com/gh/ropensci/citesdb/tree/master.svg?style=shield){data-external="1"}](https://circleci.com/gh/ropensci/citesdb)
[![](https://badges.ropensci.org/292_status.svg)](https://github.com/ropensci/software-review/issues/292)
[![codecov](https://codecov.io/gh/ropensci/citesdb/branch/master/graph/badge.svg){data-external="1"}](https://codecov.io/gh/ropensci/citesdb)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)

@@

Not to worry, just do as it says and run `cites_db_download()`. This will fetch the most recent database from online, an approximately 158 MB download. It will expand to over 1 GB in the local database. During the download and database building up to 3.5 GB of disk space may be used temporarily.

>>>>

<!-- badges: start -->

[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg){data-external="1"}](https://opensource.org/licenses/MIT)
[![Published in the Journal of Open Source Software](http://joss.theoj.org/papers/10.21105/joss.01483/status.svg){data-external="1"}](https://doi.org/10.21105/joss.01483)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2630836.svg){data-external="1"}](https://doi.org/10.5281/zenodo.2630836)
[![CircleCI](https://circleci.com/gh/ropensci/citesdb/tree/master.svg?style=shield){data-external="1"}](https://circleci.com/gh/ropensci/citesdb)
[![](https://badges.ropensci.org/292_status.svg)](https://github.com/ropensci/software-review/issues/292)
[![codecov](https://codecov.io/gh/ropensci/citesdb/branch/master/graph/badge.svg){data-external="1"}](https://codecov.io/gh/ropensci/citesdb)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)

<!-- badges: end -->

@@

Not to worry, just do as it says and run `cites_db_download()`. This will fetch the most recent database from online, an approximately 158 MB download. It will expand to over 1 GB in the local database. During the download and database building, up to 3.5 GB of disk space may be used temporarily.
